### 2020-12-17 fe_px_paper/fe_body_text.tex
Merging in Lee's feedback on the fe paper

This work presents the first measurement of several observables in this energy region, including the first independent cross sections for      \ce{^{nat}Fe}(p,x)\ce{^{52m,g}Mn},   the first measurement of \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)   isomer branching ratios via \ce{^{nat}Fe}(p,x),  and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date. 
Cumulative  \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn} reaction measurements exist in earlier work, but  this work presents the most well-characterized measurement  below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
This work is consistent with the general body of previous cumulative \ce{^{52g}Mn} measurements, with the exception of work from Williams, Lagunas-Solar, and Barchuk, all of which have shown discrepancies with prior data in other reaction channels measured here \cite{barchuk1987excitation,Lagunas-Solar1979a,PhysRev.162.1055}.

The \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) ratio seen in Figure \autoref{fig:temp_52mMn} shows significant deviation from all of the reaction models and the TENDL database near threshold, indicating potential issues with transmission particle transmission coefficients arising from the optical model.  
Above threshold the values are are all in keeping with the TENDL and default TALYS calculations and differ significantly from both the default CoH and EMPIRE calculations, indicating potential issues with the angular momentum dependence of the level density.

% Cutting as part of results reorganization
%
% For this analysis, the focus will be on the three largest channels  measured -- \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{52}Mn}.
% The use of natural abundance targets in these measurements exacerbates the modeling  challenges seen in our previous work using monoisotopic targets\,\cite{Voyles2018a}, by propagating the difficulties inherent to modeling a wide number of reaction channels, to multiple target isotopes.
% As a result, this analysis is useful for a qualitative comparison of default predictive capabilities, but no firm conclusions can be drawn about the direct causes of any inaccuracies, as there are many \enquote{moving parts} in these calculations.
% However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.
% For the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reactions, seen in \autoref{fig:51Mn}, the lower-energy  \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction, which peaks around 15\,MeV, is  well-modeled by TALYS and TENDL, and over-predicted by EMPIRE, CoH and ALICE.
% The higher-energy reactions on the higher mass Fe isotopes, however, are better matched by  EMPIRE and CoH.
% ALICE overpredicts the production of \ce{^{51}Mn} in both peaks, and appears to peak at too high an energy.
% As was seen in the modeling of high-energy proton-induced niobium reactions\,\cite{Voyles2018a}, TALYS and TENDL do well with the lower-energy \enquote{compound} reactions but do not accurately predict the higher-energy reactions that have a significant pre-equilibrium component.
% EMPIRE and CoH seem to accurately predict the locations of the peaks, but often fail to reliably estimate the magnitude of the cross section.
% This is seen again in the  
For the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, seen in Figure \autoref{fig:temp_52Mn},  the first peak is well-modeled by TALYS and TENDL, but  rises much more rapidly than the data would support above 50\,MeV.
CoH and EMPIRE, again, overpredict the cross sections at all energies, but seem to have the correct shape.
Through measurement of the  \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} independent cross section
% , seen in Figure \autoref{fig:temp_52mMn}
, the effect of spin distributions in the unresolved discrete
% highly-excited nuclear states 
can be studied.
The measured data suggest that the independent cross section to the $2^+$ isomer should be a large fraction of the cumulative cross section to \ce{^{52}Mn} (which has a $6^+$ ground state), over 50\% at the peak energy.
TALYS predictions show approximately 1.5$\sigma$ agreement with this measurement, but CoH significantly overestimates this ratio at all energies, and EMPIRE overestimates as well in the pre-equilibrium tail,   
% All three codes predict about 50\%, 
which indicates that the isomer feeding is not well-modeled in these codes.
% It is possible that this is caused by residual nucleus population and/or level density models that are skewed too heavily towards high spin.

@@

% Likewise, 
Like \ce{^{51}Mn}, \ce{Fe}(p,x) offers an interesting production pathway for  \ce{^{52}Mn}.
Conventional production uses the low-energy \ce{^{nat}Cr}/\ce{^{52}Cr}(p,n)\ce{^{52}Mn} pathways, which offer high radioisotopic purity (approximately 99.6\%)\,\cite{Graves2015,Wooten2015}.
\ce{^{nat}Fe}(p,x) offers a nearly threefold increase in production yield, but the low radioisotopic purity (99.1\% for 20--30\,MeV, decreasing to 60.8\% by 40\,MeV) at higher energies due to the opening of \ce{^{54}Mn} makes this route seem impractical.
Much like \ce{^{51}Mn}, the use of an enriched \ce{^{54}Fe} target would prevent production of \ce{^{54}Mn} and long-lived Co radiocontaminants, providing a higher-yield production route over   \ce{^{nat}Cr}(p,x), with the tradeoff of necessitating higher-energy protons ($\leq$35\,MeV) for production.
It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$~\pm~$0.003\,d\,\cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$~\pm~$0.2\,m\,\cite{Dong2015}) can be easily separated through the difference in half-life, to avoid the unfavorable gammas produced by the isomer. 
However, if nearly pure \ce{^{52m}Mn} is desired for preclinical imaging applications, the feeding of \ce{^{52}Mn} through the $\epsilon$ decay of \ce{^{52}Fe} ($t_{1/2}$ = 8.725$~\pm~$0.008\,h\,\cite{Dong2015}) exclusively populates the isomer, making this potentially suitable for production through \enquote{milking} of a \ce{^{52}Fe} generator\,\cite{Blauenstein1997}.

@@

This work presents the first measurements of several observables in 
% these mass regions.
% This work reports the first experimental measurement of
this energy region, including the measurement of the  \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions in the 0--70\,MeV region, 
the independent cross sections for      \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x), seen in \autoref{fig:58Co_IBR}. 
The cumulative cross sections from these data are both consistent with, and higher-precision than, existing measurements of the cumulative \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} cross sections, as well as the large body of measurements for \ce{^{nat}Fe}(p,x)\ce{^{56}Co}.

Despite being weakly-fed, EMPIRE, CoH, and TALYS/TENDL all do an excellent job of reproducing earlier work and this measurement, for the \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} reaction channel, as well as the strongly-fed \ce{^{nat}Fe}(p,x)\ce{^{56}Co} reaction.
This holds for both the shape and magnitude of each excitation function, though CoH overestimates the \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} peak magnitude by approximately 30\%, despite matching the rising and falling edges of the curve.
However, for both the \ce{^{nat}Fe}(p,x)\ce{^{56,58g}Co} channels, ALICE underestimates the magnitude of the rising edge and compound peak by nearly 50\%, though it shows the best agreement of these codes with the magnitude of the pre-equilibrium tails for these channels.
Additionally, all codes fail to reproduce the magnitude of the \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} peak by approximately 25\%, and completely fail to reproduce the pre-equilibrium tail for this channel, as measured in this work. 
% In 
As opposed to the other isomer-to-ground state ratio measured for Fe,  the opposite is seen for \ce{^{nat}Fe}(p,x)\ce{^{58}Co} -- the codes underpredict the ratio of the isomer-to-ground state, but in this case the isomer is the higher spin state ($5^+$, compared with a  $2^+$ ground state).
Given that the level density model was the same for all of the product nuclei, it points to the spin distribution of the initial population of the residual nucleus as the main problem with modeling, or an underestimation of high-spin transfer in pre-equilibrium neutron emission.
% However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.

Several of the activities produced via \ce{^{nat}Fe}(p,x)  could be useful as experimental monitor reactions. 
In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236~\pm~0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target. 
It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life. 
Given that \ce{^{nat}Cu}(p,x)\ce{^{56}Co} is an established monitor reaction, it seems likely that an evaluation of \ce{^{nat}Fe}(p,x)\ce{^{56}Co} as a monitor standard could provide a useful complement to existing low-to-intermediate energy monitor reactions.
A similar argument can also be applied to \ce{^{nat}Fe}(p,x)\ce{^{58}Co}, which is another established copper monitor reaction product.
While this channel shares many of the same attractive features as \ce{^{nat}Fe}(p,x)\ce{^{56}Co}, the weak feeding of \ce{^{58}Co} makes this far less of an attractive option in comparison.

In addition to the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} measurements, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications,
including the non-standard positron emitter 
% \ce{^{44}Sc}\,\cite{Muller2013,Filosofov2010,Qaim2011}
%\,\cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
\ce{^{55}Co}\,\cite{Thisgaard2011,Zaman1996,Hermanne2000a}.
% \ce{^{61}Ni}\,\cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
% \ce{^{61}Cu}\,\cite{Szelecsenyi2005a,Fukumura2004}
% \ce{^{64}Cu}\,\cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},
% \ce{^{86}Y}\,\cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
% \ce{^{89}Zr}\,\cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
% \ce{^{90}Nb}\,\cite{Busse2002,Radchenko2012},  
% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
% and the $\beta^-$-therapeutic agent 
% \ce{^{47}Sc}\,\cite{Muller2014,Deilami-nezhad2016}.
% and the Auger-therapy agent \ce{^{82\text{m}}Rb}\,\cite{Kovacs1991,Titarenko2011}. 
Production of this radionuclide offerss no major advantages over established pathways, with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x).
The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, minimizing co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
The \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} pathway shows a clear \enquote{peak} in the \ce{^{58m}Co}/\ce{^{58g}Co} branching ratio for approximately 15--30\,MeV protons, which might have translational implications if Auger electron therapy becomes more clinically prevalent.

@@

\begin{figure}[h]
 \centering
 \includegraphics[width=0.5\textwidth]{./figures/51Cr_ind.pdf}
 % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
 \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} independent cross section, with the \ce{^{56}Fe}(p,$\alpha$pn)\ce{^{51}Cr}/\ce{^{54}Fe}(p,3pn)\ce{^{51}Cr} reaction channels visibly peaking at approximately \mbox{45 MeV}.}
 \label{fig:51Cr_ind}
\end{figure}

This work presents the first measurement of \ce{^{nat}Fe}(p,x)\ce{^{49}Cr} and  the first independent cross sections for       \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} in this energy region, seen in \autoref{fig:51Cr_ind}. 
The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} cross sections, and with improved precision.
As seen in other channels, the work of Williams and Schoen \cite{PhysRev.162.1055,Schoen1979a} are both significantly lower in magnitude, and with cross sections peaking approximately 5\,MeV higher than body of other measurements. 
While the \ce{^{51}Cr} decay data used in these experiments (Williams: $t_{1/2}=27.8$ d, $I_\gamma$=9\%, Schoen: $t_{1/2}=27.71$ d, $I_\gamma$=10.2\%) differ slightly from those used here ($t_{1/2}=27.704(3)$ d, $I_\gamma$=9.910(10)\% \cite{Wang2017}), these differences do not account for the approximately 50\% smaller peak cross section reported by Williams, and approximately 30\%  smaller for Schoen. 
Neither publication reports any discussion of this channel, nor do they detail the length of each irradiation, possibly suggesting that transient equilibrium from the \ce{^{51}Mn} decay precursor was either not considered, or mis-calculated \cite{Basunia2020}.
% was not considered.

For both the  \ce{^{49,51}Cr} channels, the shape is well-modeled by all codes in the energy range covered in this measurement, though ALICE appears to peak approximately 3\,MeV higher than the other codes.
For \ce{^{49}Cr}, ALICE and CoH both overestimate the magnitude of this channel by approximately 30\%, ALICE overestimates  by approximately 350\%, while TALYS and TENDL underestimate the magnitude by approximately 50\%.
Weakly-fed channels such as \ce{^{49}Cr} are often sensitive, as the modeling of more strongly-fed channels tends to impose strong constraints upon the magnitude of remaining channels.
Modeling of \ce{^{51}Cr} shows improved agreement in magnitude --- CoH and ALICE are consistent at the 1$\sigma$ level, EMPIRE overestimates the peak by approximately 25\%, and TALYS/TENDL underestimate the peak by approximately 60\%.
However, this level of disagreement is more concerning than for \ce{^{49}Cr}, due to the strong feeding of this channel.
This observation provides a clear illustration that both TALYS/TENDL tend to either match or significantly underestimate, but never overestimate, the magnitude of many reaction channels below 70\,MeV seen in this work.
Since the sum of all channel cross sections are constrained by the total reaction cross section, this would suggest that TALYS is either overestimating the feeding of channels with stable residual nuclei, or the elastic/inelastic channels.

>>>>

This work presents the first measurement of several observables in this energy region, including independent cross sections for      \ce{^{nat}Fe}(p,x)\ce{^{52m,g}Mn},   the  \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)   isomer branching ratios via \ce{^{nat}Fe}(p,x),  as well as extending the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date. 
Cumulative  \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn} reaction measurements exist in earlier work, but  this work presents the most well-characterized measurement  below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
This work is consistent with the general body of previous cumulative \ce{^{52g}Mn} measurements, with the exception of work from Williams, Lagunas-Solar, and Barchuk, all of which have shown discrepancies with prior data in other reaction channels measured here \cite{barchuk1987excitation,Lagunas-Solar1979a,PhysRev.162.1055}.

The \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) ratio seen in Figure \autoref{fig:temp_52mMn} shows significant deviation from all of the reaction models and the TENDL database near threshold, indicating potential issues with transmission particle transmission coefficients arising from the optical model.  
Above threshold the values are are all in keeping with the TENDL and default TALYS calculations and differ significantly from both the default CoH and EMPIRE calculations, indicating potential issues with the angular momentum dependence of the level density.
% Cutting as part of results reorganization
%
% For this analysis, the focus will be on the three largest channels  measured -- \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{52}Mn}.
% The use of natural abundance targets in these measurements exacerbates the modeling  challenges seen in our previous work using monoisotopic targets\,\cite{Voyles2018a}, by propagating the difficulties inherent to modeling a wide number of reaction channels, to multiple target isotopes.
% As a result, this analysis is useful for a qualitative comparison of default predictive capabilities, but no firm conclusions can be drawn about the direct causes of any inaccuracies, as there are many \enquote{moving parts} in these calculations.
% However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.
% For the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reactions, seen in \autoref{fig:51Mn}, the lower-energy  \ce{^{54}Fe}(p,$\alpha$)\ce{^{51}Mn} reaction, which peaks around 15\,MeV, is  well-modeled by TALYS and TENDL, and over-predicted by EMPIRE, CoH and ALICE.
% The higher-energy reactions on the higher mass Fe isotopes, however, are better matched by  EMPIRE and CoH.
% ALICE overpredicts the production of \ce{^{51}Mn} in both peaks, and appears to peak at too high an energy.
% As was seen in the modeling of high-energy proton-induced niobium reactions\,\cite{Voyles2018a}, TALYS and TENDL do well with the lower-energy \enquote{compound} reactions but do not accurately predict the higher-energy reactions that have a significant pre-equilibrium component.
% EMPIRE and CoH seem to accurately predict the locations of the peaks, but often fail to reliably estimate the magnitude of the cross section.
% This is seen again in the  
For the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, seen in Figure \autoref{fig:temp_52Mn},  the  peak  at lower energy, which is largely attributable to the \ce{^{56}Fe}(p,p$\alpha$) channel, is well-modeled by TALYS and TENDL.
However, the production of \ce{^{52}Mn}  rises much more rapidly than the data would support above 50\,MeV, suggesting an overestimation of the \ce{^{56}Fe}(p,3p2n) contribution.  
CoH and EMPIRE, again, overpredict the cross sections at all energies, but seem to have the correct overall energy dependence.

Through measurement of the  \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} independent cross section
% , seen in Figure \autoref{fig:temp_52mMn}
, the effect of spin distributions in the unresolved discrete
% highly-excited nuclear 
states can be studied.
The measured data suggest that the independent cross section to the $2^+$ isomer should be a large fraction of the cumulative cross section to \ce{^{52}Mn} (which has a $6^+$ ground state), over 50\% at the peak energy.
TALYS predictions show approximately 1.5$\sigma$ agreement with this measurement, but CoH significantly overestimates this ratio at all energies, and EMPIRE overestimates as well in the pre-equilibrium tail,   
% All three codes predict about 50\%, 
which indicates that the isomer feeding is not well-modeled in these codes.
% It is possible that this is caused by residual nucleus population and/or level density models that are skewed too heavily towards high spin.

@@

% Likewise, 
% Like \ce{^{51}Mn}, 
\ce{Fe}(p,x) offers an interesting production pathway for  \ce{^{52}Mn}.
Conventional production uses the low-energy \ce{^{nat}Cr}/\ce{^{52}Cr}(p,n)\ce{^{52}Mn} pathways, which offer high radioisotopic purity (approximately 99.6\%)\,\cite{Graves2015,Wooten2015}.
\ce{^{nat}Fe}(p,x) offers a nearly threefold increase in production yield, but the lower radioisotopic purity (99.1\% for 20--30\,MeV, decreasing to 60.8\% by 40\,MeV) at higher energies due to the opening of \ce{^{54}Mn} makes this route seem impractical.
Much like \ce{^{51}Mn}, the use of an enriched \ce{^{54}Fe} target would prevent production of \ce{^{54}Mn} and long-lived Co radiocontaminants, providing a higher-yield production route over   \ce{^{nat}Cr}(p,x), with the tradeoff of necessitating higher-energy protons ($\leq$35\,MeV) for production.
It is important to note that the \ce{Fe}(p,x) route provides $\geq$60\% feeding of \ce{^{52g}Mn} ($t_{1/2}$ = 5.591$~\pm~$0.003\,d\,\cite{Dong2015}), implying that the short-lived  \ce{^{52m}Mn} ($t_{1/2}$ = 21.1$~\pm~$0.2\,m\,\cite{Dong2015}) can be easily separated through the difference in half-life, to avoid the 
% unfavorable gammas 
hard 1434\,keV gamma-ray produced by the isomer. 
However, if nearly pure \ce{^{52m}Mn} is desired for preclinical imaging applications, the feeding of \ce{^{52}Mn} through the $\epsilon$ decay of \ce{^{52}Fe} ($t_{1/2}$ = 8.725$~\pm~$0.008\,h\,\cite{Dong2015}) exclusively populates the isomer, making this potentially suitable for production through \enquote{milking} of a \ce{^{52}Fe} generator\,\cite{Blauenstein1997}.

@@

This work presents the first measurements of several observables in 
% these mass regions.
% This work reports the first experimental measurement of
this energy region, including the 
% measurement of the 
\ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions in the 0--70\,MeV region, 
the independent cross sections for      \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and the \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x), seen in \autoref{fig:58Co_IBR}. 
The cumulative cross sections from these data are both consistent with, and higher-precision than, existing measurements of the cumulative \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} cross sections, as well as the large body of measurements for \ce{^{nat}Fe}(p,x)\ce{^{56}Co}.

While it is dangerous to use weak channels to guide reaction modeling,
% Despite being weakly-fed, 
EMPIRE and TALYS/TENDL all reproduce earlier work and this measurement reasonably well ($\pm$10\%), for the \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} reaction channel, as well as the strongly-fed \ce{^{nat}Fe}(p,x)\ce{^{56}Co} reaction.
This holds for both the shape and magnitude of each excitation function.
CoH overestimates the \ce{^{nat}Fe}(p,x)\ce{^{58g}Co} peak magnitude by approximately 30\% and  \ce{^{nat}Fe}(p,x)\ce{^{56}Co}  by approximately 10\%, despite matching the rising and falling edges of the curve.
For both the \ce{^{nat}Fe}(p,x)\ce{^{56,58g}Co} channels, ALICE underestimates the magnitude of the rising edge and compound peak by nearly 50\%, though it shows the best agreement of these codes with the magnitude of the pre-equilibrium tails for these channels.

However, all codes fail to reproduce the magnitude of the \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} peak by approximately 25\%, and completely fail to reproduce the pre-equilibrium tail for this channel, as measured in this work. 
% In 
As opposed to the other isomer-to-ground state ratio measured for Fe,  the opposite is seen for \ce{^{nat}Fe}(p,x)\ce{^{58}Co} -- the codes underpredict the ratio of the isomer-to-ground state, but in this case the isomer is the higher spin state ($5^+$, compared with a  $2^+$ ground state).
Given that the level density model was the same for all of the product nuclei, it points to issues in  the spin distribution of the initial population of the residual nucleus 
% as the main problem with modeling, or an underestimation of high-spin transfer 
in the pre-equilibrium neutron emission.
% However, no firm conclusions can be drawn about the direct causes of the inaccuracies, as there are many \enquote{moving parts} in these calculations, with measurements performed using natural abundance targets.

The \ce{^{nat}Fe}(p,x)\ce{^{56}Co} channel ($t_{1/2}=77.236~\pm~0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})
% Several of the activities produced via \ce{^{nat}Fe}(p,x)  
could be useful as an experimental monitor reaction  due to its high intensity and production of long-lived residual products that produce bright decay gamma-rays. 
% In particular, \ce{^{nat}Fe}(p,x)\ce{^{56}Co} ($t_{1/2}=77.236~\pm~0.026$ d, $\epsilon$=100\% to \ce{^{56}Fe}\,\cite{Junde2011})  is a strongly-fed reaction channel (peak cross section of approximately 400\,mb near 12\,MeV), with a sufficiently-long half-life permitting offline gamma spectrometry,  and  cannot be populated via secondary neutrons incident upon the monitor target. 
% It possesses a number of intense gamma-rays, which are distinct from those populated by daughter states in the decay of  \ce{^{56}Mn}, and the gammas which are produced both in the decay of  \ce{^{56}Co} and  \ce{^{56}Mn} may be easily resolved based on differences in intensity and half-life. 
Given that \ce{^{nat}Cu}(p,x)\ce{^{56}Co} is an established monitor reaction, it seems likely that an evaluation of \ce{^{nat}Fe}(p,x)\ce{^{56}Co} as a monitor standard could provide a useful complement to existing low-to-intermediate energy monitor reactions.
A similar argument can also be applied to \ce{^{nat}Fe}(p,x)\ce{^{58}Co}, which is another established copper monitor reaction product.
While this channel shares many of the same attractive features as \ce{^{nat}Fe}(p,x)\ce{^{56}Co}, the weak feeding of \ce{^{58}Co} makes this far less of an attractive option in comparison.

In addition to the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} measurements, this experiment has also yielded production cross section  measurements of  a number of additional  emerging radionuclides with medical applications,
including the non-standard positron emitter 
% \ce{^{44}Sc}\,\cite{Muller2013,Filosofov2010,Qaim2011}
%\,\cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
\ce{^{55}Co}\,\cite{Thisgaard2011,Zaman1996,Hermanne2000a}.
% \ce{^{61}Ni}\,\cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
% \ce{^{61}Cu}\,\cite{Szelecsenyi2005a,Fukumura2004}
% \ce{^{64}Cu}\,\cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},
% \ce{^{86}Y}\,\cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
% \ce{^{89}Zr}\,\cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
% \ce{^{90}Nb}\,\cite{Busse2002,Radchenko2012},  
% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
% and the $\beta^-$-therapeutic agent 
% \ce{^{47}Sc}\,\cite{Muller2014,Deilami-nezhad2016}.
% and the Auger-therapy agent \ce{^{82\text{m}}Rb}\,\cite{Kovacs1991,Titarenko2011}. 
Production of this radionuclide offerss no major advantages over established pathways, with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x).
The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, lowering the  co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
The \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} pathway shows a clear \enquote{peak} in the \ce{^{58m}Co}/\ce{^{58g}Co} branching ratio for approximately 15--30\,MeV protons, which might have translational implications if Auger electron therapy becomes more clinically prevalent.

@@

% \begin{figure}[h]
%  \centering
%  \includegraphics[width=0.5\textwidth]{./figures/51Cr_ind.pdf}
%  % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
%  \caption{Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} independent cross section, with the \ce{^{56}Fe}(p,$\alpha$pn)\ce{^{51}Cr}/\ce{^{54}Fe}(p,3pn)\ce{^{51}Cr} reaction channels visibly peaking at approximately \mbox{45 MeV}.}
%  \label{fig:51Cr_ind}
% \end{figure}

\begin{figure*}
    \centering
    \subfloat{
        \centering
        \hspace{-5pt}\subfigimg[width=0.485\textwidth]{\hspace{4.5cm}a)}{./figures/49Cr.pdf}{50}
%         \caption{ Decay curve for the isomeric transition of \ce{^{115m}In}.}
         %         \refstepcounter{subfigure}
         \label{fig:fig49Cr}
   \hspace{-5pt}}%
     \subfloat{
        \centering

        \subfigimg[width=0.485\textwidth]{\hspace{4.5cm}b)}{./figures/51Cr_ind.pdf}{50}
         %         \refstepcounter{subfigure}
         \label{fig:fig51Cr}
   \hspace{-5pt}}%
    \caption{a) Measured \ce{^{nat}Fe}(p,x)\ce{^{49}Cr} independent cross section, with the \ce{^{56}Fe}(p,$\alpha$p3n)\ce{^{49}Cr}/\ce{^{54}Fe}(p,3p3n)\ce{^{49}Cr} reaction channels visibly peaking at approximately \mbox{48 MeV}.   b) Measured \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} independent cross section, with the \ce{^{56}Fe}(p,$\alpha$pn)\ce{^{51}Cr}/\ce{^{54}Fe}(p,3pn)\ce{^{51}Cr} reaction channels visibly peaking at approximately \mbox{45 MeV}.} 
     \label{fig:51Cr_ind}
\end{figure*}

This work presents the first measurement of \ce{^{nat}Fe}(p,x)\ce{^{49}Cr} and  the first independent cross sections for       \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} in this energy region, seen in \autoref{fig:51Cr_ind}. 
The cumulative cross sections from these data are also consistent with existing measurements of the cumulative \ce{^{nat}Fe}(p,x)\ce{^{51}Cr} cross sections, and with improved precision.
As seen in other channels, the work of Williams and Schoen \cite{PhysRev.162.1055,Schoen1979a} are both significantly lower in magnitude, and with cross sections peaking approximately 5\,MeV higher than body of other measurements. 
While the \ce{^{51}Cr} decay data used in these experiments (Williams: $t_{1/2}=27.8$ d, $I_\gamma$=9\%, Schoen: $t_{1/2}=27.71$ d, $I_\gamma$=10.2\%) differ slightly from those used here ($t_{1/2}=27.704(3)$ d, $I_\gamma$=9.910(10)\% \cite{Wang2017}), these differences do not account for the approximately 50\% smaller peak cross section reported by Williams, and  30\%  smaller for Schoen. 
Neither publication reports any discussion of this channel, nor do they detail the length of each irradiation,  suggesting that transient equilibrium from the \ce{^{51}Mn} decay precursor was either not considered, or mis-calculated \cite{Basunia2020}.
% was not considered.

For both the  \ce{^{49,51}Cr} channels, the shape is well-modeled by all codes in the energy range covered in this measurement, though ALICE appears to peak approximately 3\,MeV higher than the other codes.
For \ce{^{49}Cr}, ALICE and CoH both overestimate the magnitude of this channel by approximately 30\%, ALICE overestimates  by approximately 350\%, while TALYS and TENDL underestimate the magnitude by approximately 50\%.
% Weakly-fed channels such as \ce{^{49}Cr} are often sensitive, as the modeling of more strongly-fed channels tends to impose strong constraints upon the magnitude of remaining channels.
However, it should be noted that weakly-produced nuclides should not be used to guide reaction modeling due to their sensitivity to stronger reaction channels.
Modeling of \ce{^{51}Cr} shows improved agreement in magnitude --- CoH and ALICE are consistent at the 1$\sigma$ level, EMPIRE overestimates the peak by approximately 25\%, and TALYS/TENDL underestimate the peak by approximately 60\%.
However, this level of disagreement is more concerning than for \ce{^{49}Cr}, due to the strong feeding of this channel.
This observation provides a clear illustration that both TALYS/TENDL tend to either match or significantly underestimate, but never overestimate, the magnitude of many reaction channels below 70\,MeV seen in this work.
Since the sum of all channel cross sections are constrained by the total reaction cross section, this would suggest that TALYS is either overestimating the feeding of channels with stable residual nuclei, or the elastic/inelastic channels.
